### 2021-09-03 documentos/pce.tex
microavance

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The first one is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving is required for the process $\mcE$ to be deterministic, this
is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local character of quantum theory. This is, with positivity of the map
$\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
$\Delta\geq 0$. In the other hand, complete positvity of $\mcE$ reads $\id_k
\otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state
between the system and an ancilla with Hilbert space $\hilbert_k$. Therefore,
complete positivity ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators, trace preserving is automatically
fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
where $\mcE$ acts locally, is send to a valid density matrix, this is the
substance of complete positivity.

Quantum channels \ddnote{[Choi representation, Kraus operators and Stinespring
dilation]}

>>>>

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The first one is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving is required for the process $\mcE$ to be deterministic, this
is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local character of quantum theory. This is, with positivity of the map
$\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
$\Delta\geq 0$. In the other hand, complete positvity of $\mcE$ reads $\id_k
\otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state
between the system and an ancilla with Hilbert space $\hilbert_k$. Therefore,
complete positivity ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators, trace preserving is automatically
fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.

Quantum channels can be characterized by means of the Choi-\jami{} isomorphism~\cite{choi,jamil}. Given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.

  \ddnote{[Choi representation, Kraus operators and Stinespring
dilation]}
